### 2016-09-20 image_setup.tex
minor change
fixed line numbers

\Suppressnumber\begin{lstlisting}[]
# sed -i '/^exit 0/i bash /home/pi/rasp_config/update_rasp_config' ${ROOTDIR}/etc/rc.local
\end{lstlisting}
\FloatBarrier
\vspace{-5mm}

@@

%\todot{insert sed command below instead}
\Suppressnumber\begin{lstlisting}[]
# sed -i '/^exit 0/i bash /home/pi/rasp_config/main' ${ROOTDIR}/etc/rc.local
\end{lstlisting}
\FloatBarrier
\vspace{-5mm}

@@

The Raspbian lite image should now be possible to use almost as if it had
been booted in a \ac{Raspi}. A major difference is that the testbed
administrator \ac{PC} is likely significantly faster than a \ac{Raspi}.
Hence, enabling updates, upgrades and installing new software packages
should be faster than in a \ac{Raspi}. Still updating and upgrading
the packages for the \ac{Raspi} might take some amount of time. To get
the upgraded system packages, it is necessary to run:

>>>>

\begin{lstlisting}[]
# sed -i '/^exit 0/i bash /home/pi/rasp_config/update_rasp_config' ${ROOTDIR}/etc/rc.local
\end{lstlisting}
\FloatBarrier
\vspace{-5mm}

@@

%\todot{insert sed command below instead}
\begin{lstlisting}[]
# sed -i '/^exit 0/i bash /home/pi/rasp_config/main' ${ROOTDIR}/etc/rc.local
\end{lstlisting}
\FloatBarrier
\vspace{-5mm}

@@

The Raspbian lite image should now be possible to use almost as if it had
been booted in a \ac{Raspi}. A major difference is that the testbed
administrator \ac{PC} is likely significantly faster than a \ac{Raspi}.
Hence, enabling updates, upgrades and installing new software packages
should be faster than in a \ac{Raspi}. Still updating and upgrading
the packages for the \ac{Raspi} might take some amount of time.
To get the upgraded system packages, it is necessary to run:
%To update the system package list, run the following command:
